High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
issues with formatting for MLJFlux

    ces = Dict()
    for (mod_name, mod) in model_dict
        ce = generate_counterfactual(
            x, target, counterfactual_data, mod, eccco_generator; 
            decision_threshold=γ, max_iter=T,
            initialization=:identity,
            converge_when=:generator_conditions,
        )
        ces[mod_name] = ce
    end
    _plt_order = map(x -> findall(collect(keys(model_dict)) .== x)[1], plt_order)

@@

	front = Flux.Chain(
			   Conv((k, k), n_channels => c1, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Conv((k, k), c1 => c2, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Flux.flatten)
	d = Flux.outputsize(front, (n_in..., n_channels, 1)) |> first
    back = Flux.Chain(
        Dense(256, 120, relu),
        Dense(120, 84, relu),
        Dense(84, n_out),
    )
	return Flux.Chain(front, back)
end

@@

add_models = Dict(
    "Large Ensemble" => mlp_large_ens,
    "LeNet-5" => lenet,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble", 
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

>>>>

    ces = Dict()
    for (mod_name, mod) in model_dict
        if mod.model.model isa ProbabilisticPipeline
            x = mod.model.model.f(x)
            _data = counterfactual_data
            _data.X = mod.model.model.f(_data.X)
        end
        ce = generate_counterfactual(
            x, target, counterfactual_data, mod, eccco_generator; 
            decision_threshold=γ, max_iter=T,
            initialization=:identity,
            converge_when=:generator_conditions,
        )
        ces[mod_name] = ce
    end
    _plt_order = map(x -> findall(collect(keys(model_dict)) .== x)[1], plt_order)

@@

	front = Flux.Chain(
        Conv((k, k), n_channels => c1, pad=(p, p), relu),
        MaxPool((2, 2)),
        Conv((k, k), c1 => c2, pad=(p, p), relu),
        MaxPool((2, 2)),
        Flux.flatten
    )
	d = Flux.outputsize(front, (n_in..., n_channels, 1)) |> first
    back = Flux.Chain(
        Dense(d, 120, relu),
        Dense(120, 84, relu),
        Dense(84, n_out),
    )

    chain = Flux.Chain(front, back)

	return chain
end

@@

add_models = Dict(
    "LeNet-5" => lenet,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```
